### 2021-04-26 SupplementaryMaterial/Vita.tex
Updates from Overleaf

    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Quincunx: Measuring Side-channel Vulnerabilities
    By Fuzzing and Memory Auditing'', under review.

@@

>>>>

    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Measuring Side-channel Vulnerabilities
    By Fuzzing and Memory Auditing'', under review.

@@

    \item Zihao Wang, Pei Wang, \textbf{Qinkun Bao}, and Dinghao Wu, ``Inferring Complex Grammars with Static Program Analysis'', under review.
